Distance Sampling in \proglang{R}

### 2015-12-05 paper.Rmd
add readdst

>>>>

Distance for Windows has many users (**STAT HERE**) and they may be overwhelmed by the prospect of switching existing analyses to \proglang{R}. For that reason we have created the \pkg{readdst} package to interface with projects created by Distance for Windows'. The package can take analyses created using the CDS, MCDS and MRDS engines in Distance for Windows and extract data and create equivalent model definitions. \pkg{readdst} can also run these analyses and test the resulting statistics (for example, $\hat{N}$ or $\hat{P_a}$) calculated in \proglang{R} against those calculated by Distance for Windows. We hope that \pkg{readdst} will provide a useful transition to \proglang{R} for interested users. \pkg{readdst} is currently available on GitHub at \url{https://github.com/distancedevelopment/readdst}.
